\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-10-22 fully-abstract-comp/popl2019/paper.tex
Rephrase reference to CHERI ISA a bit.

In this work, we propose and study \stktokens{}: an alternative calling convention that enforces WBCF and LSE with a single shared stack.
Instead of CHERI's local capabilities, it builds on {\itshape linear} capabilities; a new form of capabilities that has not previously been described in the published literature, although a design sketch for them is incorporated in the latest CHERI ISA reference~\citep{TODO}\todo{reference!} and related ideas have been described by~\citet[``scarce objects'']{szabo_formalizing_1997,szabo_scarce_objects} and in technical documents.
% KJAA: Perhaps make it clear by who and when/where?
The hardware prevents these capabilities from being duplicated.
We propose to make stack and return pointers linear and require components to hand them out in cross-component invocations and to return them in returns.
The non-duplicability of linear capabilities together with some security checks allow us to guarantee WBCF and LSE without large overhead on boundary crossings and in particular without the need for clearing large blocks of memory.

@@

\todo{Watson et al.\ (XXX: fix name to reflect citation) have concurrently developed an extension of the CHERI-MIPS instruction set with linear capabilities.}
\todo{\url{https://nakamotoinstitute.org/scarce-objects/}}
\todo{\url{http://journals.uic.edu/ojs/index.php/fm/article/view/548}}

>>>>

In this work, we propose and study \stktokens{}: an alternative calling convention that enforces WBCF and LSE with a single shared stack.
Instead of CHERI's local capabilities, it builds on {\itshape linear} capabilities; a new form of capabilities that has not previously been described in the published literature, although related ideas have been described by~\citet[``scarce objects'']{szabo_formalizing_1997,szabo_scarce_objects} and in technical documents.
Concurrently with our work, Watson et al. have developed a (more realistic) design for linear capabilities in CHERI that will be incorporated in the latest CHERI ISA reference~\citep{TODO}\todo{reference!}.
% KJAA: Perhaps make it clear by who and when/where?
The hardware prevents these capabilities from being duplicated.
We propose to make stack and return pointers linear and require components to hand them out in cross-component invocations and to return them in returns.
The non-duplicability of linear capabilities together with some security checks allow us to guarantee WBCF and LSE without large overhead on boundary crossings and in particular without the need for clearing large blocks of memory.

@@
